Visit Scotland Notebook

### 2023-06-16 draft_work.Rmd
Minor Aesthetic Changes To A Range of Plots

>>>>

library(broom)
library(factoextra)

international_summary <- international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         !country %in% c("USA", "Germany")) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits)
  # filter(total_visits > 500,
  #        spend_per_visit > 0.5)

international_clust <- international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         !country %in% c("USA", "Germany")) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>% 
  # filter(total_visits > 500,
  #        spend_per_visit > 0.5) %>% 
  select(total_visits, spend_per_visit)

k_clusters <- tibble(k = 1:63) %>% 
  mutate(kclust = map(k, ~ kmeans(international_clust,
                                  centers = .x,
                                  nstart = 25)),
         tidied = map(kclust, tidy),
         glanced = map(kclust, glance),
         augmented = map(kclust, augment, international_summary))

```{r}
fviz_nbclust(international_clust,
             kmeans,
             method = "wss", #within sum of squares
             nstart = 25)
```

```{r}
fviz_nbclust(international_clust,
             kmeans,
             method = "silhouette",
             nstart = 25)
```

```{r}
clusterings %>% 
  unnest(augmented) %>% # Unnest augmented created in step 5.1
  filter(k == 2) %>% # Set number of clusters
  ggplot(aes(x = total_visits, y = spend_per_visit, colour = .cluster)) +
  geom_point()
```

```{r}
clusterings %>% 
  unnest(augmented) %>% # Unnest augmented created in step 5.1
  filter(k == 4) %>% 
  group_by(.cluster) %>% 
  filter(.cluster == 2)
```

### 2023-06-16 visit_scotland_notebook.Rmd
Minor Aesthetic Changes To A Range of Plots

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1) +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Average")

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1) +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Average")

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = nights)) +
  geom_line(group = 1) +
  geom_point(aes(colour = nights_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Nights (Thousands) \n",
       title = "Average Annual Nights Stayed by Domestic Vistors",
       subtitle = "3 Year Average")

@@

```{r}
regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = exp_per_visit)) +
  geom_line(group = 1) +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "3x Year Average Expenditure per Visit (Thousands) \n",
       title = "Average Expenditure Per Visit Domestic Vistors",
       subtitle = "3 Year Average")
```

@@

>>>>

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Average") +
  ylim(0, 13000)

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Average") +
  ylim(0, 3500)

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = nights)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Nights (Thousands) \n",
       title = "Average Annual Nights Stayed by Domestic Vistors",
       subtitle = "3 Year Average")

@@

```{r}
regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = exp_per_visit)) +
  geom_line(group = 1, size = 1, colour = "#540453") +
  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "3x Year Average Expenditure per Visit (Thousands) \n",
       title = "Average Expenditure Per Visit Domestic Vistors",
       subtitle = "3 Year Average")
```

@@

##### Mean Spend Per Visit Plot
